A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-03-09 main.tex
Updates from Overleaf

\subsubsection{TCIA validation}
https://wiki.cancerimagingarchive.net/display/Public/TCGA-HNSC
https://cancer.digitalslidearchive.org/#!/CDSA/hnsc/TCGA-BA-4076/TCGA-BA-4076-01A-01-BS1?slide=TCGA-BA-4076-01A-01-BS1.4aef481c-f634-4ffc-9fb3-609f59a8caf9.svs
TCGA Pathology Images => The Cancer Imaging Archive (TCIA) by Deep learning (R/Keras framework)
%數位模擬，能讓臨床醫師和研究人員更快速了解細胞成長後的狀況，而不是花費時間等待細胞的培養。
image-based phenotypes and their underlying genomic data 
https://www.biorxiv.org/content/10.1101/2020.03.10.985887v1.full
https://github.com/Serian1992/ImgBio.

@@

*** interpretable or explainable CNN
Manning meap book: 不再是黑盒子
https://www.manning.com/books/trust-in-machine-learning
Trust in Machine Learning

*** 必備 explainable interpretable 
By saliency mapping: e.x. diabetes retinopathy, model focused on retinal aterry

@@

Understanding the Method Behind the Machine
interpredability

@@

%% TCGA new holistic features %%%%%
In summary of our current study, those 10 candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in our \acrshort{hnscc} study.
Thus, the prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort. The important input $X_1...X_n$ should be patients' features: age, specific 10 gene expressions, clinical T stage, and surgical margin so far.
When we consider the survival prediction model again,
ground truth Y (e.x. patient's survival):\\[0.5cm]
%Y$:\\[0.3cm]
$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$\\
gene expression is not an independent $X_mrna$, which could be correlated with other $X_body, X_stress, X_fear, X_meaningOfLife, X_inflammation, X_ros$ factors.
There is much work to be done in investigating the functional network more fully\cite{Rogers1959}.
%We wish the TCGA does collect more holistic features from their participants in the future.
%依舊是以管窺天
% https://link.springer.com/referenceworkentry/10.1007%2F978-1-4419-1428-6_575
%癌症與身心靈的重要關係：中醫、citation? emotional centered approach
We suggest TCGA should cover more holistic features:
cortisol is one of the most common objective outcome studied in psychoneuroimmunological (PNI) factors. Other factors usually are interleukin, cytokines, lymphocytes (CD4+, CD8+), CD56+, vitals signs, telomere length, telomere activity, HRV.
The standardized, psychosocial (subjective) measures includes depression, stress, quality of life, anxiety, fatigue, mindfulness, mood and specific spiritual growth (ie, meaning of life)\cite{Hsiao2012}.
%冤親債主的意念 unknown X factors 回到我們的文章
Since sychological benefit (reduction of stress, fatigue, sleep disturbance, and depressive symptoms) also optimizes immune function (higher natural killer cell activity, higher \acrshort{ifng}, lower TNF-alpha, lower IL-6) in terms of better survival of cancer patients.

>>>>

\subsubsection{TCIA validation}
%https://wiki.cancerimagingarchive.net/display/Public/TCGA-HNSC
%https://cancer.digitalslidearchive.org/#!/CDSA/hnsc/TCGA-BA-4076/TCGA-BA-4076-01A-01-BS1?slide=TCGA-BA-4076-01A-01-BS1.4aef481c-f634-4ffc-9fb3-609f59a8caf9.svs
TCGA Pathology Images => The Cancer Imaging Archive (TCIA) by Deep learning (R/Keras framework)
%數位模擬，能讓臨床醫師和研究人員更快速了解細胞成長後的狀況，而不是花費時間等待細胞的培養。
image-based phenotypes and their underlying genomic data 
%https://www.biorxiv.org/content/10.1101/2020.03.10.985887v1.full
%https://github.com/Serian1992/ImgBio.

@@

*** interpretable or explainable CNN
%Manning meap book: 不再是黑盒子
%https://www.manning.com/books/trust-in-machine-learning
Trust in Machine Learning

%*** 必備 explainable interpretable 
By saliency mapping: e.x. diabetes retinopathy, model focused on retinal aterry

@@

Understanding the Method Behind the Machine: interpredability

@@

%% TCGA new holistic features %%%%%
In summary of our current study, those 10 candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in our \acrshort{hnscc} study.
Thus, the prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort. The important input $X_1...X_n$ should be patients' features: age, specific 10 gene expressions, clinical T stage, and surgical margin so far.
When we consider the survival prediction model again,
ground truth Y (e.x. patient's survival):\\[0.5cm]
%Y$:\\[0.3cm]
$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$\\
gene expression is not an independent $X_mrna$, which could be correlated with other $X_{body}, X_{stress}, X_{fear}, X_{meaningOfLife}, X_{inflammation}, X_{ros}$ factors.
There is much work to be done in investigating the functional network more fully\cite{Rogers1959}.
%We wish the TCGA does collect more holistic features from their participants in the future.
%依舊是以管窺天
% https://link.springer.com/referenceworkentry/10.1007%2F978-1-4419-1428-6_575
%癌症與身心靈的重要關係：中醫、citation? emotional centered approach
We suggest TCGA should cover more holistic features:
cortisol is one of the most common objective outcome studied in psychoneuroimmunological (PNI) factors. Other factors usually are interleukin, cytokines, lymphocytes (CD4+, CD8+), CD56+, vitals signs, telomere length, telomere activity, HRV.
The standardized, psychosocial (subjective) measures includes depression, stress, quality of life, anxiety, fatigue, mindfulness, mood and specific spiritual growth (ie, meaning of life)\cite{Hsiao2012}.
%冤親債主的意念 unknown X factors 回到我們的文章
Since psychological benefit (reduction of stress, fatigue, sleep disturbance, and depressive symptoms) also optimizes immune function (higher natural killer cell activity, higher \acrshort{ifng}, lower TNF-alpha, lower IL-6) in terms of better survival of cancer patients.
